\section{Output Error model}
Time to do the math now. Let's assume that the rider only excerts steering torque and knows the configuration of the bicycle $\mathbf{q}$. The rol angle $\phi_c$ is considered the control objective and no external excitation is present. In this case, the steering torque is expected to be some function of the desired roll angle and configuration of the bicycle:
		\begin{align}
		T_\delta = {K}(\mathbf{q},\phi_c)
		\end{align}
At this point the function could be of any form, it could be linear/non-linear,  may include differentials/integrals, could be discontinues/continues, include time delays, etc. %A block form representation is given in the figure below.
%\input{images/block_general}
\subsection{Parametric models}
Next the human controller is modelled as a parametric model. This is achieved by assuming a solution of any form, which can be optimized by changing the values of the parameter vector $\boldsymbol{\theta}$. The parameterized model is given by:
		\begin{align}
		\hat{T}_\delta = \hat{K}(\boldsymbol{\theta},\mathbf{q},\phi_c)
		\end{align}
\subsection{Output error model}
The output error model is used to compare the measured data with the model simulation data. The model returns the error between the outputs of the two systems. In order to apply this method, one should measure the steering torque and bicycle configuration. The desired roll angle is determined to be zero, which corresponds to balancing the bike in an upright position. The measured configuration $\mathbf{q}$ is then inserted in the parametric model, which outputs steering torque $\hat{T}_\delta$. The error $e(t)$ is defined as the difference between the measured and modelled simulation data. The resulting model is shown in the block diagram (\ref{fig:OE}). Finally, the following well known criterium function is set up to determine the quality of the fit:
    \input{images/block_outputerror}
		\begin{align}
		J = \frac{1}{2}\sum_i\left(\tilde{T}_{\delta,i} - \hat{T}_{\delta,i} \right)^2
		\end{align}
This criterium can be used to compare different models for the human controllers. A value of zero indicates a perfect fit, whereas higher values of $J$ indicate larger errors. The criterium function can also be used to optimize the model parameter vector.


%\subsection{Application}
%Next we will apply the output error method on the obtained dataset and the model of dr. Hess. 
%\subsection{Human limitations}
%Inherently the human as it's limiations, it is not a perfect controller. Humans have a limited sensory system, which includes sensory noise $n$. In addition the motor ouput also contains some output noise $w$. For sake of simplicity we will assume these uncertainties to be Gaussian distributed. To make things worse, human sensory and motor systems are known to contain time delays.
%\subsection{Observer model}
%In this section it is described how humans estimate the state based on a internal model of the bicycle combined with their limited sensory systems. In control theory an optimal version of state estimation is called a Kalman observer. This observer is optimal in the sense that is tries to find a least square solution of the state. A simple version of this observer assumes linearity, acts continuesly and can be modified to include time delays. Let's assume humans are smart and therefore behave like the Kalman observer. The working principle of a Kallman optimal observer is yet to be described in this section. 
%\subsection{Control models}
%Even altough we assumed a linear continues obserer model, the controller still can be discontinues and non llinear. For example; the observer can work continuesly while the controllers acts intermittently (as A. Doyle suggested). 